---
title: "AG Hackathon Notebook"
output: html_notebook
---

Get libraries
```{r}
library(readr)
library("dplyr")
library("tidyr")
library("ggplot2")
```


Import data
```{r}
books <- read_csv("/Users/thandekachehore/Documents/GitHub/allangrayhackathon/ML/books.csv")
booksActive = as_tibble(books) %>% filter(language_code %in% c("eng", "en-US", "en-GB", "en-CA"))
```

View data
```{r}
summary(booksActive) #quantitative summary of table
head(booksActive) #first 5 results
```

List top 10 books with more than 10 ratings

```{r}
top10BooksRatings = top_n(booksActive, 10, ratings_count) %>% 
  select(title, authors, average_rating, language_code, ratings_count)
```

Get Books from 5 specific languages
- Germany, French, eng-us, eng-gb, eng
```{r}
BooksLang =  booksActive %>% filter(language_code %in% c("eng", "en-US", "en-GB", "en-CA")) #filter by 5 conditions of languages
```

-Get number of authors
-Count number of books by each of the top 10 authors
-Top 10 highly rated authors
-Bottom least rated authors
```{r}

```


Import second dataset
Turn dataset into  tibble
connect the two datasets
divide the values in a column by a separator

